---
title: 'EDS 241: Assignment 1'
author: 'Javier Patrón'
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

Question 1:

Application of estimators based on the "treatment ignorability"
assumption The goal is to estimate the causal effect of maternal smoking
during pregnancy on infant birth weight using the treatment ignorability
assumptions (Lecture 6 & 7).

The data are taken from the National Natality Detail Files, and the
extract "SMOKING_EDS241.csv"' is a random sample of all births in
Pennsylvania during 1989-1991. Each observation is a mother-infant pair.
The key variables are:

The outcome and treatment variables are:

-   birthwgt = birth weight of infant in grams

-   tobacco = indicator for maternal smoking

The control variables are: mage (mother's age), meduc (mother's
education), mblack (=1 if mother black), alcohol (=1 if consumed alcohol
during pregnancy), first (=1 if first child), diabete (=1 if mother
diabetic), anemia (=1 if mother anemic)

Load in the libraries

```{r}
library(tidyverse)

```

Load in the data

```{r}
smoke <- read_csv(here::here("SMOKING_EDS241.csv"))

```

(a) What is the unadjusted mean difference in birth weight of infants
with smoking and nonsmoking mothers? Under what assumption does this
correspond to the average treatment effect of maternal smoking during
pregnancy on infant birth weight? Provide some simple empirical evidence
for or against this assumption.

```{r}
#Question (a)



```

(b) Assume that maternal smoking is randomly assigned conditional on the
observable covariates listed above. Estimate the effect of maternal
smoking on birth weight using an OLS regression with linear controls for
the covariates. Report the estimated coefficient on tobacco and its
standard error.

```{r}
# Question (b)


```

(c) Use the exact matching estimator to estimate the effect of maternal
smoking on birth weight. For simplicity, consider the following
covariates in your matching estimator: create a 0-1 indicator for
mother's age (=1 if mage\>=34), and a 0-1 indicator for mother's
education (1 if meduc\>=16), mother's race (mblack), and alcohol
consumption indicator (alcohol). These 4 covariates will create 2 \* 2
*\** 2 \* 2 = 16 cells.

```{r}
# Question (c)


```

Report the estimated average treatment effect of smoking on birthweight
using the exact matching estimator and its linear regression analogue.
